### 2017-09-07 paper/related.tex
pass on related work

%% \textit{Usage of massively parallel hardware:}
\textit{Hardware level parallelization:} Previous research
investigated the feasibility of testing embedded software on Graphics
Processing Units (GPUs) as an alternative to multicore
CPUs~\cite{rajan-etal-ase2014}.  The Simple Instruction Multiple Data
(SIMD) architecture of modern GPUs allows running the same test case
with different test data over several threads.  Although benchmarks
indicate far superior performance over traditional multicore CPUs,
there are severe limitations. Control-flow branching in source code
can impact performance negatively while violating the lock-step
execution during the divergence of instructions~\cite{rajan-etal-ase2014}
%% existing GPU programming-models (\eg{}, CUDA~\cite{cuda}, and
%% OpenCL~\cite{opencl}) are compatible only with a subset of the C/C++
%% language.
Recent work proposed a compiler-assisted approach to make programs
compatible with the relying programming-model used by
GPUs to parallelize tests~\cite{yaneva-etal-issta2017}.

\Jbc{...Justify they are out of scope for our subjects...}.

>>>>

%% \textit{Usage of massively parallel hardware:}
\textit{Hardware level massive parallelization:} Previous research
investigated the feasibility of testing embedded software on Graphics
Processing Units (GPUs) as an alternative to multicore
CPUs~\cite{rajan-etal-ase2014}.  The Simple Instruction Multiple Data
(SIMD) architecture of modern GPUs allows running the same test case
with different test data over several threads.  Although benchmarks
indicate far superior performance over traditional multicore CPUs,
there are severe limitations. Control-flow branching in source code
can impact performance negatively while violating the lock-step
execution during the divergence of instructions~\cite{rajan-etal-ase2014}
%% existing GPU programming-models (\eg{}, CUDA~\cite{cuda}, and
%% OpenCL~\cite{opencl}) are compatible only with a subset of the C/C++
%% language.
Recent work proposed a compiler-assisted approach to make programs
compatible with the relying programming-model used by
GPUs to parallelize tests~\cite{yaneva-etal-issta2017}.
\Jbc{...Justify they are out of scope for our subjects...}.
